---
title: "Hello R world post"
description-meta: "{{< meta website.description >}}"
date: "2017-01-29"
categories: [r]
---


Welcome to my blog!

My name is Ilya, I am a demographer. Here I plan to post some research related stuff. As I am crazy about [R](https://www.r-project.org), my post will touch upon this tool/environment -- I will share some tricks and cool visualizations. Eventually, I hope to contribute to the amazing [R-bloggers](https://www.r-bloggers.com) project. First, I am going to post older bits -- to gain momentum. 

***
Just to start with, let me show you a small and handy self-written R function.   
Quite often, visualizing data in R, we compose color palettes manually. It is nice to have a function that shows the actual colors of a vector with color values. Here it is.


```{r}
glimpse_colors <- function(colors_string){
        n <- length(colors_string)
        hist(1:n, breaks = 0:n, col = colors_string)
}
```

The function takes a vector of colors as input and produces a basic uniform histogram with one bar for each color, filled accordingly. Let's try it out. First, we create some colors, and then visualize them.   

```{r}
library(RColorBrewer)
pal <- brewer.pal(n = 9, name = 'BrBG')
glimpse_colors(pal)
```


Enjoy!

P.S. If something similar exists in one of the well known packages, please tell me.

